Results

### 2023-02-15 06_Paper/ER-ED/ERED_Stage2/method.Rmd
Chi-squared

To investigate whether individual SVs predict ER choice (H7a), a Chi-squared test with predicted choice (highest SV of each participant) and actual choice was computed.
Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy was computed.

>>>>

To investigate whether individual SVs predict ER choice (H7a), a $\chi{2}$ test with predicted choice (highest SV of each participant) and actual choice was computed.
Furthermore, an ordinal logistic regression with the dependent variable choice and independent variables SVs of each strategy was computed.
